Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-20 Corrected_version.tex
correction

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{aligned}
&\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
&\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
&
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps}

=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{aligned}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

@@

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{aligned}
&\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
&\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
&
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps} 
=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{aligned}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

@@

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
